%\section{Discussion and Summary}
This document has detailed the development and deployment of a
sophisticated de-identification tool for clinical reports, designed to
ensure privacy and compliance with health data regulations. Through
rigorous testing, including a focused case study at the University
Hospital Zurich, the tool has demonstrated high effectiveness in
recognizing and anonymizing personal health information
(PHI).

{\bf Notably, the tool achieves over 99\% recall in identifying and
  anonymizing 'Contact', 'Date', and 'Name' entities, and
  approximately 95\% for 'Age', with 'Location' entities recognized
  with about 91\% recall.} These results underscore the tool's robust
capability to safeguard sensitive information.  Challenges remain in
the lower recall rates for 'ID' and 'Occupation', which are 85\% and
64\%, respectively. However, these entities are considered less
critical from a privacy standpoint as 'ID' numbers appear infrequently
and occupations are generally not too specific. {\bf If a recall
  threshold of at least 90\% is set as a benchmark for privacy
  concerns, this tool reliably removes critical PHI categories such as
  Age, Contact, Date, Location, and Names.}

Future improvements will focus on enhancing the tool's machine
learning models to better understand contextual nuances and reduce
false positives, thereby increasing the reliability of the
de-identification process. This ongoing enhancement will ensure that
the tool not only meets the regulatory requirements but also adapts
efficiently to varied data formats and clinical environments,
maintaining high standards of patient privacy without compromising the
utility of the data for research and clinical review.

